\problemname{Witch Dance}
Each Halloween, the $N$ witches of Sweden all gather high up in the air with their brooms to perform a magical dance.
The dance consists of taking one's broom and rotating clockwise around one of the ends of the broom.
Each broom is exactly $1\text{ m}$ long, and everyone rotates at the same speed.
The $i$'th witch originally starts rotated $r_i\text{ radians}$ clockwise.
All the witches are located at the same height in the air, at positions $(x_i, y_i)$ for $1 \le i \le N$.

This dance is very beautiful, but has in recent years been plagued by a certain problem.
It turns out that nobody had choreographed the dance properly.
This caused some of the witches to crash into each other's brooms.
As a result, their brooms would break and they would fall down helplessly, being forced to use their parachutes -- can you imagine a greater embarrassment for a witch?

This year, a coalition of witches are tired of their brooms breaking.
They have thus produced a choreography beforehand, consisting of the original locations and rotations of the witches' brooms.
Can you check if the dance will cause any brooms to crash into each other?

\section*{Input}
The first line of input consists of a single integer $N$ ($1 \le N \le 200\,000$), the number of witches.
The next $N$ lines contains a description of each broom.
Each line consists of the floating-point numbers $x_i, y_i$ ($-10^{9} \le x_i \le y_i 10^{9}$), and the floating-point number $r_i$ ($0 \le r_i < 2\pi$).
The coordinates are measured in meters, and give you the end of the broom that the broom rotates around.

\section*{Output}
Output \texttt{ok} if no witches will crash into each other, and \texttt{crash} if at least one pair of witches will crash.
