\problemname{Cupcakes}
Ylva loves cupcakes, probably more than anything else on this planet.
She loves them so much that she baked a large plate of $R \cdot C$ cupcakes for her \emph{fikaraster}\footnote{``Fikarast'' is a Swedish word, meaning to take a break from work while enjoying coffee and pastries together with your colleagues.}.

Ylva has a large wooden tray which can fit $R$ rows of $C$ cupcakes per row, that she will put the cupcakes on.
Her cupcakes have three different topping: Nutella Buttercream, Red Wine Chocolate Ganache, and Strawberry Whipped Cream.
Since Ylva is a master cupcakeer, she knows that presentation is $90\%$ of the execution.
In particular, it looks very bad if two cupcakes of the same color are adjacent to each other within a row or a column on the tray.
We call an arrangement of cupcakes where this is never the case a \emph{good arrangement}.

Given the number of cupcakes of each flavour, and the size of Ylva's tray, can you help her find a good arrangement of the cupcakes, or determine that no such arrangement exists?

\section*{Input}
The first line of input contains the two space-separated integers $2 \le R, C \le 1000$.
The next line contains three non-negative space-separated integers $A, B, C$ -- the number of cupcakes of the three flavours which Ylva has baked.
It is guaranteed that $A + B + C = R \cdot C$.
Both $R$ and $C$ will be even.

\section*{Output}
If no good arrangement can be found, output \texttt{impossible}.
Otherwise, output $R$ lines, each containing $C$ characters, representing a good arrangement.
Each row should contain only characters \texttt{A, B, C}, depending on which flavour should be placed on a certain position.
The number of \texttt{A} cupcakes placed must be equal to $A$, and so on.
