\problemname{Closing the Schools}
Your country, home to a population of $10\,000\,000$ people, is currently facing a a viral epidemic.
As of now (on day $0$), a single person in the country, Patty Ent the Zeroth, is infected.
If there are $Y$ persons infected one day, $Y$ new people (or all the remaining uninfected one, if this is less than $Y$) are infected the next day.
A patient is sick during 14 days, including the day on which they are infected.

Your health services can cope with $Z$ people being sick at any given time.
To avoid the exponential spread of the new virus and overwhelming the health services, your government have a single counter-measure - they can close down the schools.
During the days during which the schools are closed down, only $0.1Y$ new people are infected for that day.
Unfortunately, closing down the schools carries a huge societal cost - each day of closure costs the government 10 billion SEK!
Furthermore, schools can only be closed down once, and will remain closed until the last person has recovered from the disease.

Your task is to determine the minimum number of days schools must be closed in order ot not overwhelm the health services.

\section*{Input}
The first and only line of input contains the integer $Z$ -- the capacity of your health care.

\section*{Output}
If the health services would be overwhelmed even if closing down the schools on day $1$, output \texttt{chaos}.

Otherwise, output the minimum number of days schools must be closed.
